paper1_results_figs_slimmed_50_rr

### 2016-06-27 inst/documents/keep_old_insecticide.Rmd
rename correct mix & male exposure inputs

#add these for extended analysis
if (experiment=='extended')
  treePredictors <- c(treePredictors,'maleExposureProp','correctMixDeployProp')

@@

#create a curtisInputs dataframe for use later
curtisInputs <- data.frame("exposure"=0.9,
                           "effectiveness_insecticide1"=0.73,
                           "effectiveness_insecticide2"=1,
                           "start_freq_allele1"=0.01,
                           "start_freq_allele2"=0.01,
                           "dominance_allele1"=0.17,
                           "dominance_allele2"=0.0016,
                           "selection_coef_allele1"=0.23,
                           "selection_coef_allele2"=0.43,
                           "maleExposureProp"=1,
                           "correctMixDeployProp"=1,
                           "resist_start_lo_div_hi"=1,
                           "resist_start_1_div_2"=1)

>>>>

#add these for extended analysis
if (experiment=='extended')
  treePredictors <- c(treePredictors,'male_exposure_prop','correct_mix_deploy')

@@

#create a curtisInputs dataframe for use later
curtisInputs <- data.frame("exposure"=0.9,
                           "effectiveness_insecticide1"=0.73,
                           "effectiveness_insecticide2"=1,
                           "start_freq_allele1"=0.01,
                           "start_freq_allele2"=0.01,
                           "dominance_allele1"=0.17,
                           "dominance_allele2"=0.0016,
                           "selection_coef_allele1"=0.23,
                           "selection_coef_allele2"=0.43,
                           "male_exposure_prop"=1,
                           "correct_mix_deploy"=1,
                           "resist_start_lo_div_hi"=1,
                           "resist_start_1_div_2"=1)

### 2016-06-27 inst/documents/paper1_results_figs.Rmd
moved documents into own folder
rename correct mix & male exposure inputs

@@

    #modify killer plot mix2 vs seq to add in male exposure prop on x axis
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure+exposure*maleExposureProp, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.25))+

             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure+exposure*maleExposureProp, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides for both sexes') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

>>>>

```{r, eval=FALSE, echo=FALSE, fig.height=3.5}

  #10/5/2016 seems to crash R, so set to eval=FALSE

@@

    #modify killer plot mix2 vs seq to add in male exposure prop on x axis
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure+exposure*male_exposure_prop, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.25))+

             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure+exposure*male_exposure_prop, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides for both sexes') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

### 2016-06-27 inst/documents/paper1_results_figs_rr.Rmd
rename correct mix & male exposure inputs

  #create a curtisInputs dataframe for use later
  curtisInputs <- data.frame("exposure"=0.9,
                             "effectiveness_insecticide1"=0.73,
                             "effectiveness_insecticide2"=1,
                             "effectiveness_added"=1.73,                             
                             "start_freq_allele1"=0.01,
                             "start_freq_allele2"=0.01,
                             "dominance_allele1"=0.17,
                             "dominance_allele2"=0.0016,
                             "dominance_added"=0.1716,                             
                             # 14/6/16 rr_advantage = s / effectiveness
                             #"selection_coef_allele1"=0.23,
                             #"selection_coef_allele2"=0.43,
                             "rr_advantage_I1"=0.23/0.73,
                             "rr_advantage_I2"=0.43/1,                             
                             "maleExposureProp"=1,
                             "correctMixDeployProp"=1,
                             "resist_start_lo_div_hi"=1,
                             "resist_start_1_div_2"=1)

@@

    #modify killer plot mix2 vs seq to add in male exposure prop on x axis
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure+exposure*maleExposureProp, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.5))+

             facet_grid( ~ seq_better_mix20.5, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure+exposure*maleExposureProp, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides for both sexes') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

>>>>

  #create a curtisInputs dataframe for use later
  curtisInputs <- data.frame("exposure"=0.9,
                             "effectiveness_insecticide1"=0.73,
                             "effectiveness_insecticide2"=1,
                             "effectiveness_added"=1.73,                             
                             "start_freq_allele1"=0.01,
                             "start_freq_allele2"=0.01,
                             "dominance_allele1"=0.17,
                             "dominance_allele2"=0.0016,
                             "dominance_added"=0.1716,                             
                             # 14/6/16 rr_advantage = s / effectiveness
                             #"selection_coef_allele1"=0.23,
                             #"selection_coef_allele2"=0.43,
                             "rr_advantage_I1"=0.23/0.73,
                             "rr_advantage_I2"=0.43/1,                             
                             "male_exposure_prop"=1,
                             "correct_mix_deploy"=1,
                             "resist_start_lo_div_hi"=1,
                             "resist_start_1_div_2"=1)

@@

    #modify killer plot mix2 vs seq to add in male exposure prop on x axis
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure+exposure*male_exposure_prop, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.5))+

             facet_grid( ~ seq_better_mix20.5, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure+exposure*male_exposure_prop, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides for both sexes') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

### 2016-06-27 inst/documents/paper1_results_figs_slimmed.Rmd
rename correct mix & male exposure inputs

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
              "dominance_allele1","selection_coef_allele1","maleExposureProp")
  out_cols <- c("time_to_resistance0.25","strategy")
  ggSubset <- ggSubset[, c(in_cols,out_cols) ]

>>>>

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
              "dominance_allele1","selection_coef_allele1","male_exposure_prop")
  out_cols <- c("time_to_resistance0.25","strategy")
  ggSubset <- ggSubset[, c(in_cols,out_cols) ]

### 2016-06-27 inst/documents/paper1_results_figs_slimmed_50.Rmd
rename correct mix & male exposure inputs

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
  #             "dominance_allele1","selection_coef_allele1","maleExposureProp")
  in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")

>>>>

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
  #             "dominance_allele1","selection_coef_allele1","male_exposure_prop")
  in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")

### 2016-06-27 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
rename correct mix & male exposure inputs

  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
  #             "dominance_allele1","selection_coef_allele1","maleExposureProp")
  #in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")  
  in_cols <- c("exposure","effectiveness_added","dominance_added")

>>>>

  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
  #             "dominance_allele1","selection_coef_allele1","male_exposure_prop")
  #in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")  
  in_cols <- c("exposure","effectiveness_added","dominance_added")
